---
title: "Data Structures"
output:
  html_document:
    df_print: paged
---

# Your Turn #1
# (Variables & Assignment)

Guess what this code will do, and then run it.

Also: Take a look at the "Environment" tab, both before and after running the code.
Also: Note that we are using both = and <- for assignment. Is there a difference?

```{r}
stock_price = 100
print(stock_price)

stock_price <- 99
print(stock_price)
```

# Your Turn #2
# (Create a Vector)

Create a vector that contains 3 numbers:
1. The year Christopher Columbus sailed the ocean blue
2. The year America became an independent country
3. The year you started working at MarketBridge

Store the values in a variable named "years". Then print it out.
```{r}

```

# Your Turn #3
# (Create a Named Vector)

Create a vector called `years_named` that contains the exact same data as `years`. But each element should have a name that describes what happened that year. Then print out the vector.

# Example
# stock_price_history = c(
#   "Jan" = 98,
#   "Feb" = 99,
#   "Mar" = 100)
# print(stock_price_history)
```{r}
```

# Your Turn #4
# (Vector Indexing)

You are given a vector `words` that form the sentence "Your name is Ari".

1. Using indexing, change the last word to be your name, not mine. 
2. Create a new vector, `words_question`, that forms the sentence "is Your name Ari". Use indexing to access each individual word of the original vector.

```{r}
words = c("Your", "name", "is", "Ari")
words[ <index> ] = "<your name>"
print(words)

words_question = c(words[3], ...)
print(words_question)
```

# Your Turn #5
# (Vectorized Operations)

Create a vector called `years` that contains 3 numbers: 
1. The year Christopher Columbus sailed the ocean blue
2. The year America became an independent country
3. The year you started working at MarketBridge

Then create a new vector, `years_since`, that contains the years since the first event that each event happened. Create `years_since` by performing a vectorized operation on `years`.

```{r}

years        = c(1492, 1776, 2021)
years_since  = ...

```

# Your Turn #6
# (Creating a Data Frame)

Create two vectors: `events` and `years`:
1. `events` should contains the words "columbus", "usa", "mb"
2. `years` should contain the years Columbus sailed the ocean blue, the year the US became independent and the year you joined market bridge.

Then create a data frame with those vectors as columns.

Then print the result.

# Syntax reminder:
# df = data.frame(col1 = c("a", "b", "c"), col2 = c(1, 2, 3))

```{r}

```

# Your Turn #7
# (Manipulating Data Frame Columns)

I have given you a data frame which contains events and the years in which they occurred. 
1. Modify the dataframe to have the correct years for these events.
2. Create a new column called "years_since" which contains the years since 1492 in which these happened. years_since should be created via a vectorized operation on the "year" column
3. Delete the "year" column
4. print the result

```{r}
events = c("columbus", "usa", "mb")
years  = c(1492, 1776, 2021)

df = data.frame(event = events, 
                year  = years)

```